---
title: "Case Study 2"
author: "Thad Schwebke"
date: "4/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Rubric

Due April 18th

- 30% RMarkdown File
- 30% Final Video Presentation (15% slide content, 15% presentation)
	- Minimal Stumbles / mis statements / etc.  if you trip up more than a couple of times, reshoot the video. It will be much better with the practice!
	- Labeled Plots
	- 7-minute time limit
	- Correct interpretation
	- Complete analysis – this means adding pvalues and conducting tests where appropriate (I expect everyone to have a good handle on at least t-tests, KNN and Naïve Bayes     classification and KNN and linear regression to this point.  
- 10% Validation Requirement for Attrition(Sensitivity > 60% and Specificity > 60%)
- 10% Validation Requirement for Salary(RMSE < $3000)
- 10% Creativity and completeness in presentation and analysis.
- 10% Knit RMD and YouTube link on a tab on your GitHub Site.

## Description

DDSAnalytics is an analytics company that specializes in talent management solutions for Fortune 100 companies. Talent management is defined as the iterative process of developing and retaining employees. It may include workforce planning, employee training programs, identifying high-potential employees and reducing/preventing voluntary employee turnover (attrition). To gain a competitive edge over its competition, DDSAnalytics is planning to leverage data science for talent management. The executive leadership has identified predicting employee turnover as its first application of data science for talent management. Before the business green lights the project, they have tasked your data science team to conduct an analysis of existing employee data. 

## Presentation

You have been given a dataset (CaseStudy2-data.csv) to do a data analysis to identify factors that lead to attrition.  
- You should identify the top three factors that contribute to turnover (backed up by evidence provided by analysis). There may or may not be a need to create derived attributes/variables/features. 

- The business is also interested in learning about any job role specific trends that may exist in the data set (e.g., “Data Scientists have the highest job satisfaction”). 

- You can also provide any other interesting trends and observations from your analysis. 

The analysis should be backed up by robust experimentation and appropriate visualization. Experiments and analysis must be conducted in R. 

- You will also be asked to build a model to predict attrition.
- Record and upload to YouTube a 7-minute presentation


## Predictions

I provided an additional data set of 300 observations that do not have the labels (attrition or not attrition).  We will refer to this data set as the “Competition Set” and is in the file “CaseStudy2CompSet No Attrition.csv”.  I have the real labels and will thus assess the accuracy rate of your best classification model. 10% of your grade will depend on the sensitivity and specificity rate of your “best” classification model for identifying attrition.  

- You must provide a model that will attain at least 60% sensitivity and specificity (60 each = 120 total) for the training and the validation set.  Therefore, you must provide the labels (ordered by ID) in a csv file.  Please include this in your GitHub repository and call the file “Case2PredictionsXXXX Attrition.csv”.  XXXX is your last name.  (Example: Case2PredictionsSadler Attrition.csv” would be mine.)  An example submission file can be found on GitHub: Case2PredictionsClassifyEXAMPLE.csv.

I have also provided an additional data set of 300 observations that do not have the Monthly Incomes.  This data is in the file “CaseStudy2CompSet No Salary.csv”.  I have the real monthly incomes (salaries) and will thus assess the RMSE regression model. 10% of your grade will depend on the RMSE (Root Mean square error) of your final model.

- You must provide a model that will attain a RMSE < $3000 for the training and the validation set.  Therefore, you must provide the predicted salaries (ordered by ID) in a csv file.  Please include this in your GitHub repository and call the file “Case2PredictionsXXXX Salary.csv”.  XXXX is your last name.  (Example: Case2PredictionsSadler Salary.csv” would be mine.)  An example submission file can be found on GitHub: Case2PredictionsRegressEXAMPLE.csv.

Notes on models to fit: IMPORTANT: First and foremost, you may use outside models that we have not covered but it must be in addition to models that we have covered in class. This means for classifying attrition, you must use either k-NN or naive Bayes but may also use other models (logistic regression, random forest, LDA, SVM, etc) as long as you compare the results between the two or more models.  You may then use any of the models to fulfill the 60/60 sensitivity/specificity requirement.  This goes for regression as well; you must use linear regression but may include additional models for comparison and use in the competition (LASSO, random forest, ensemble models, etc.).  

## Documents and Files

- Create a GitHub repository named CaseStudy2DDS with an RMarkdown file containing an executive summary, introduction to the project, all supporting code and analysis, and the slides for the presentation.  The repository should also include your prediction csv file and don’t forget to put the link to the YouTube video in the RMarkdown file.

- Submit a link to the GitHub repository via the space provided for the Case Study 02 page in 2DS. 

- Finally, make sure put the link to the YouTube video on the Google Doc.  

- Finally, create a Knit file out of your RMD and display it on your GitHub Site you created in Unit 12.  Include the link to your Youtube video (and a link to your RShiny app too if there is one!)

- Create an RShiny App to help visualize you results.  The amount of bonus points awarded will be based on correctness, creativeness, effectiveness of the visualization / app. 

## Bonus

The data scientist with the highest sensitivity + specificity (both at least 60%) on the classification validation set will win the Bonus: 5 extra points and bragging rights!  This bonus is between all 4 sections.  1 prize between all 40+ students. 

The data scientist with the lowest RMSE on the regression validation set will win the Bonus: 5 extra points and bragging rights!  This bonus is between all 4 sections.  1 prize between all 40+ students.

## FAQ and Comments

1.  Question: In the dataset, what does Relationship Satisfaction mean...(relationship to manager, to peers) Relationship satisfaction with manager. 
•	Advice: Don't eliminate variables simply because they have a high correlation with one another.  This is an indication that they do share some information although the information they don't share may be correlated with the response individually.  
•	Advice: When plotting and exploring attrition, the percentage of those who left is probably more useful than the count.  

2. Question: In the dataset, is the distance from home in miles or kilos?
We don't have that information (however we do know whether its high or low)

3.  Question: In the dataset: what is the definition of pay rates: Hourly, Daily & Monthly.  These values to not seem to relate to each other or the Monthly Salary (which is different than Monthly Rate).
We don't have that information (however we do know whether they are high or low). They may or may not relate to each other or the monthly salary (this is for the student to infer and decide whether theres any correlation or whether this is a useful feature for attrition)

4. Question: In the dataset: we do see that Job Levels go from 1-5 and assume that 1 may symbolize a lower level employee, but this is not defined.  Though this level does have a positive linear relationship with Monthly Income, it does not seem to correlate well with the Job Titles. in other words someone with a Director can be a 2-5, and manager a 3-5.
Yes we can assume 1 is a lower job level than 5. 

5. Question: In the dataset, does overtime mean Hourly vs. Salaried worker?
We can assume that people with overtime are non-exempt employees. 

6. Question: In the dataset, Performance Ratings are only 3 & 4, is there a mistake?  Unless a corrupted system, hard to imagine ratings consistently high, even as 2 still means "good". It is self-reported data, think about why the employees may only answer 3 and 4
No this is the only data we have, there is no mistake. 

7. Question: In the dataset, does Training times mean: hours, weeks, or instances and over what period?
Training times last year means number of training sessions attended by the employee. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
